PAGAI : a path sensitive static analyser

### 2012-05-18 papers/TAPAS2012/pagai.tex
typo

It is well know fact in abstract interpretation that the least upper bound of two or
more abstract values in the abstract domain 
may induce unrecoverable loss of precision. This operation typically occurs with
if-then-else statements and loops.

>>>>

It is well know in abstract interpretation that the least upper bound of two or
more abstract values in the abstract domain 
may induce unrecoverable loss of precision. This operation typically occurs with
if-then-else statements and loops.
